Stage-Splitting a Modal Language

### 2014-08-14 paper/semantics.tex
refine the metatheorems

\TODO explain that the $\vdash_\bbtwo$ judgments are for \langTwo.

@@

\TODO fix the next theorem:

\begin{theorem}
If $\Gamma\vdash\xi\wf$ and
$\Gamma,\dom\xi\vdash \colone{v}{A}$ and
$\Gamma,\dom\xi\vdash v\pval$
then 
$\reify{\xi}{v}{q}$ and
$\typeslangTwo q A$.
\end{theorem}

>>>>

Recall that residuals live in \langTwo; we will indicate typing judgments in
\langTwo\ with $\vdash_\bbtwo$.

@@

\begin{theorem}
If $\Gamma\vdash\xi\wf$ and
$\Gamma,\dom\xi\vdash \colone{\next\ \hat y}{\fut A}$
then 
$\reify{\xi}{\hat y}{q}$ and
$\typeslangTwo q A$.
\end{theorem}

\TODO
We want to generalize the previous theorem to all 1-types, not just $\fut A$,
but then we must value-split the partial value, and then we don't know the type
of the output. (?)

\begin{theorem}
If $\Gamma\vdash\xi\wf$ and
$\Gamma,\dom\xi\vdash \colone{v}{A}$ and
$\Gamma,\dom\xi\vdash v\pval$
then
$v \vsplito [v_1,v_2]$ and
$A$ type-splits to $A_1,A_2$ and
$\reify{\xi}{v_2}{q}$ and
$\typeslangTwo q A_2$.
\end{theorem}
